### 2019-06-05 doc/chapters/introduction.tex
added text

@@

A powerful method to check whether a program works correctly is formal verification.
This is a systematic process based on mathematical modeling.
With formal verification all possible inputs are explored algorithmically and exhaustively.
This is in contrast to testing, where only predefined inputs are tested.
The correctness of a program is analyzed relative to its formal specification.
Formal specification is a mathematical description of a software behavior that can be used by the verification tool to verify the code. \cite{sanghavi:formal_verification}

@@

In the work some fragments of the code of Bitcoin-S has to be verified.
Bitcoin-S is an open source Scala implementation of the Bitcoin protocol. 
There are different projects belonging to Bitcoin-S.
Protocol data structures are defined in the package \textbf{bitcoin-s-core}.
This package is the main target to be verified because it specifies the base of Bitcoin protocol, and it is crucial for correct protocol functionality.
There is also the package \textbf{bitcoind-rpc} which is an RPC client implementation to communicate with \textit{bitcoind}, daemon of Bitcoin Core running on a machine.
Developers of Bitcoin-S are working on the implementation of a lightweight bitcoin client in the package \textbf{bitcoin-s-spv-node}.
The whole list of packages can be found on GitHub\footnote{\url{https://github.com/bitcoin-s}}.

>>>>

// TODO move to chapter description and change Overview of stainless to formal verification with stainless

@@

A powerful method to check whether a program works correctly is formal verification.
This is a systematic process based on mathematical modeling.
With formal verification all possible inputs are covered algorithmically.
This is in contrast to testing, where only predefined inputs are tested.
The correctness of a program is analyzed relative to its formal specification.
Formal specification is a mathematical description of a software behavior that can be used by the verification tool to verify the code.
We will see an example shortly.

@@

In the work we verify some fragments of the code of Bitcoin-S.
Bitcoin-S is an open source Scala implementation of the Bitcoin protocol. 
There are different projects belonging to Bitcoin-S.
Protocol data structures are defined in the package \textbf{bitcoin-s-core}.
This package is the main target to be verified because it specifies the base of Bitcoin protocol, and it is crucial for correct protocol functionality.
There is also the package \textbf{bitcoind-rpc} which is an RPC client implementation to communicate with \textit{bitcoind}, daemon of Bitcoin Core running on a machine.
Developers of Bitcoin-S are working on the implementation of a lightweight bitcoin client in the package \textbf{bitcoin-s-spv-node}.
The whole list of packages can be found on GitHub\footnote{\url{https://github.com/bitcoin-s}}.
